% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage[english]{babel}
\usepackage[bookmarks=true,pdfborder={0 0 0}]{hyperref}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{color}
\usepackage{array}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{enumitem}

%\usepackage{titlesec}

\makeatletter
\providecommand{\tabularnewline}{\\}
\date{}

\renewcommand{\dblfloatpagefraction}{0.95}
\renewcommand{\floatpagefraction}{0.95}

% (jsun): this adds the section symbol in front of section references 
%\renewcommand*{\p@section}{\S\,}
%\renewcommand*{\p@subsection}{\S\,}

\setlength{\belowcaptionskip}{-1ex}
\usepackage{listings}
\lstset{
    basicstyle=\small\ttfamily,
    tabsize=2,
    columns=fullflexible,
    keepspaces=true,
    language=c
}

\renewcommand{\paragraph}{%
  \@startsection{paragraph}{4}%
  {\z@}{1ex \@plus 1ex \@minus .2ex}{-1em}%
  {\normalfont\normalsize\bfseries}%
}

\makeatother
\usepackage{listings}
\renewcommand{\lstlistingname}{Listing}

\begin{document}
\title{\Large \bf Spiffy: Enabling File-System Aware Storage Applications}
\author{
  {\rm Kuei Sun, Daniel Fryer, Matthew Lakier, Joseph Chu, Angela Demke Brown and Ashvin Goel}\\
  University of Toronto
%  \and
%      {\rm Daniel Fryer}\\
%      University of Toronto
%  \and
%      {\rm Matthew Lakier}\\
%      University of Toronto
%  \and
%      {\rm Angela Demke Brown}\\
%      University of Toronto
%  \and
%      {\rm Ashvin Goel}\\
%      University of Toronto
} % end author

\maketitle

\begin{abstract}
Many file-system applications such as defragmentation tools, file system checkers or data recovery tools, operate at the storage layer. Today, developers of these storage applications require detailed knowledge of the file-system format, which takes a significant amount of time to learn, often by trial and error, due to insufficient documentation or specification of the format. Furthermore, these applications perform ad-hoc processing of the file-system metadata, leading to bugs and vulnerabilities. 

% All of these hurdles impede the development of innovative file-system application by reducing potential developers to those who also work on the file systems themselves.
% (jsun): don't really like the above sentence. Not sure if it emphasized the point that we could lower 
% the bar for building fs apps by making it eaiser to work with fs metadata.

We propose Spiffy, an annotation language for specifying the on-disk format of a file system. File-system developers annotate the data structures of a file system, and we use these annotations to generate a library that allows identifying, parsing and traversing file-system metadata, providing support for both offline and online storage applications. This approach simplifies the development of storage applications that work across different file systems because it reduces the amount of file-system specific code that needs to be written.

%
% (jsun): don't actually need to itemize all of the tools, just the cool ones
%
We have written annotations for the Linux Ext4, Btrfs and F2FS file systems, and developed several applications for these file systems, including a type-specific metadata corruptor, a file system converter, and an online storage layer cache that preferentially caches files for certain users. 
Our experiments show that applications that use the library to access file system metadata can achieve good performance and are robust against file system corruption errors.

\end{abstract}

\input{introduction.tex}
\input{motivation.tex}
\input{approach.tex}
\input{applications.tex}
\input{implementation.tex}
\input{evaluation.tex}
\input{related_work.tex}

%\section{Future Work\label{sec:Future_Work}}

%In the current version of our file system conversion tool, a power failure while overwriting the metadata of the source file system would permanently corrupt it. We plan to add failure atomicity to the tool in the next iteration.

%Spiffy currently has no semantic understanding of file system metadata, which requires application developers to write file-system specific code.  However, there are common concepts between file system such as the notion of files and directories, and the allocation of blocks, even though each file system may choose different format to represent these concepts.  To bridge the semantic gap, we are working on a new interface which enables writing truly file-system agnostic applications by identifying these commonalities.  Application developers can use the interface to perform tasks such as allocating a new block, and copying content to it, all without knowing the underlying file system implementation.

\section{Conclusion\label{sec:Conclusion}}

Spiffy is an annotation language for specifying the on-disk file system data structures. File system developers annotate their data structures using Spiffy, which enables generating a library that allows parsing and traversing file system data structures correctly.

%We have demonstrated the simplicity and expressiveness of the language, and 
We have shown the generality of our approach by annotating three vastly different file systems. The annotated file system code serves as a detailed documentation for the metadata structures and the relationships between them. File-system aware storage applications can use the Spiffy libraries to improve their resilience against parsing bugs, and to reduce the overall programming effort needed for supporting file-system specific logic in these applications. Our evaluation suggests that applications using the generated libraries perform reasonably well. We believe our approach will enable interesting applications that require an understanding of storage structures.

\section*{Acknowledgements}
We thank the anonymous reviewers and our shepherd, Andr\'e Brinkmann, for 
their valuable feedback. This work was supported by NSERC.

{\footnotesize \bibliographystyle{acm}
\bibliography{bibliography}}
%\input{language.tex}

\end{document}

